Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-11 doc/JFLA2022/paper.tex
fix a few typos

Since the set \textit{AP} of additive principals  is closed under addition
(by Lemma \textit{AP\_plus\_closed}), it suffices to prove the inequalities $\omega<\phi_0(2)$ and $42<\phi_0(2)$.

>>>>

Since the set \textit{AP} of additive principals  is closed under addition
(by Lemma \textit{AP\_plus\_closed}), it suffices to prove the inequalities $\omega<\omega^2$ and $42<\omega^2$.
